%
%Copyright (c) 2005-2021 Imperas Software Ltd., www.imperas.com
%
%The contents of this file are provided under the Software License Agreement
%that you accepted before downloading this file.
%
%This header forms part of the Software but may be included and used unaltered
%in derivative works.
%
%For more information, please visit www.OVPworld.org or www.imperas.com
%
This document provides the details of an extension library for an OVP Fast Processor Model.
\par
OVP Fast Processor Models are written in C and provide a C API for use in C based
platforms. The models also provide a native interface for use in SystemC TLM2 platforms.
\par
The models are written using the OVP VMI API that provides a Virtual Machine Interface that defines the behavior of the processor.
The VMI API makes a clear line between model and simulator allowing very good optimization and world class high speed performance.
Most models are provided as a binary shared object and also as source.
This allows the download and use of the model binary or the use of the source to explore and modify the model.
\par
The models are run through an extensive QA and regression testing process and most model families are validated using technology provided by the processor IP owners.
There is a companion document (OVP Guide to Using Processor Models) which explains the general concepts of OVP Fast Processor Models and their use.
It is downloadable from the OVPworld website documentation pages.
\par
\setlength{\parindent}{0pt}

